Piecewise Regression for Nutritional Outcomes Pre- and Post-CFTR Modulator

### 2022-05-15 StatNet/knot_models.qmd
Update knot_models.qmd

```{r}
#| include: false
# Load libraries, data, etc.
library(DiagrammeR)
library(MultiKink)
library(ggplot2)
library(broom)
library(knitr)
data("triceps")
```

@@

---

@@

```{r}
tri.age.plot = ggplot(triceps,aes(x = age,y = triceps)) + geom_point(alpha = 0.5) +
  xlab("Age") + ylab("Triceps") + theme_bw()
tri.age.plot
```

---

@@

@@

```{r}
kable(triceps[c(which(triceps$age<5)[1],which(triceps$age<10&triceps$age>5)[1],
          which(triceps$age>20&triceps$age>10)[1]),],row.names = F)
```

---

@@

The estimates of c5, c10, and c20 indicate change in slope at the respective knot.

@@

>>>>

```{r}
#| include: false
# Load libraries, data, etc.
library(DiagrammeR)
library(MultiKink)
library(ggplot2)
library(broom)
library(knitr)
data("triceps")
cf = read.csv("/Users/timvigers/GitHub/CF/StatNet/data.csv",
              stringsAsFactors = F,na.strings = "")
```

@@

------------------------------------------------------------------------

@@

```{r}
tri.age.plot = ggplot(triceps,aes(x = age,y = triceps)) + geom_point(alpha = 0.6) +
  xlab("Age") + ylab("Triceps") + theme_bw()
tri.age.plot
```

------------------------------------------------------------------------

@@

-   Can add these values by hand easily (using the difference \* an indicator):

@@

-   Examples of what the new variables should look like:

```{r}
kable(triceps[c(which(triceps$age<5)[1],which(triceps$age<10&triceps$age>5)[1],
          which(triceps$age<20&triceps$age>10)[1],
          which(triceps$age>=20)[1]),c("age","c5","c10","c20")],row.names = F)
```

------------------------------------------------------------------------

@@

\
The estimates of c5, c10, and c20 indicate change in slope at each respective knot.

## Pre-/Post-CFTR Data

@@

## Vitamin A Plot

```{r}
vita_plot = ggplot(cf,aes(x = Time,y = Vitamin.A,color = factor(Patient.ID))) + 
  geom_point(alpha = 0.6) +
  ylab("Vitamin A") + theme_bw() + theme(legend.position = "none")
```

```{r}
mod = lmer(Vitamin.A ~ Time + c1 + c2 + (1|Patient.ID),data = cf)
```

### To Do

-   Change missing c2 values to 0

-   Write out mixed model with two knots

-   Summarize results

## A Bayesian Approach
